\subsection{Purpose of the system}
		The purpose of our calendar system is to replace the old fashioned paper calendar with a twist. The calendar stands out in its ability to set up appointments between strangers. When creating an appointment, it is possible to leave room for extra unknown participants to be added to appointment by our server. These "lucky" participants will, in their own calendar, create an "empty" appointment, a so called lucky appointment, where they want to be invited to a random event, at a certain time, in a specified city. That way people seeking, for instance participants for a street party, a bingo tournament or even a 4th player in a tennis double match, will be able to find their extra participants. And people lacking something to do while on a business trip to a foreign city, or simply someone who is bored on a Saturday, will get an invitation to try something new, with new and exiting people.

		We call it - LuckyCalendar.

\subsection{Scope of the system}

\subsection{Objectives and success citeria the project}

\subsection{Definitions, acronyms and abbreveations}

\subsection{References}


Version system:\\
First decimal increments whenever we have made complete changes. \\
Second decimal increments for every major change (Not addition).   \\
Third decimal increments for every minor change or major addition.\\

{\tabulinesep=1.2mm
\begin{tabu}{ | p{1.4cm} | p{1.2cm} | p{1.3cm} | p{2.2cm} | p{7cm} |}
    \hline
    Date 		&	Version	& 	Initials			&	Title				&	Description    \\ \hline
    18/09/14	& 	0.1.0	&	pawh, mrfm, hstb	&	Assignment	37		&	Elementary design, use cases and generic calendar functionality.\\ \hline
    20/09/14	& 	0.2.0	&	pawh, mrfm, hstb	&	LuckyCalender		&	We have made some major changes to the overall idea of the calendar by adding the idea of LuckyAppointments to the calendar. We have begun on the object analysis of the system.\\ \hline
    21/09/14	& 	0.2.1	&	hstb			&	Sequence Diagram 	&	Added a sequence diagram and renamed the system to LuckyCalendar, so we know the difference between our system and the calendar.\\ \hline
    22/09/14	& 	0.2.2	&	hstb			&	State Machine Diagram 	&	Added a state machine diagram for appointment\\ \hline
    22/09/14	& 	0.2.3	&	pawh, mrfm,hstb	&	Assignment	38	&	Changes to State machine and class diagram, in order to handle appointments missing LuckyParticipants.\\ \hline
    02/10/14	& 	0.2.4	&	hstb			&	Assignment	39	&	Updated the class diagram to match the SDD.\\ \hline
\end{tabu}
}\\\\
VersionControl for minor changes and additions:
https://github.com/Madsen90/BDSA/commits/master
\subsection{Overview}